\begin{blocksection}
\question
Suppose we have int *A that points to the head of an array of length len. 
Determine which statement (A)-(E) correctly describes the code execution and provide a one or two sentence justification.

\begin{parts}

\part
Consider the following code:
\begin{verbatim}
#pragma omp parallel for
for (int x = 0; x < len; x++){
    *A = x; 
    A++;
}
\end{verbatim}
Is the code: \\
A) Always Incorrect \\
B) Sometimes Incorrect \\ 
C) Always Correct, Slower than Serial \\
D) Always Correct, Speed relative to Serial depends on Caching Scheme \\
E) Always Correct, Faster than Serial \\

\begin{solution}[0.5in]
B \\
Justification:
The for loop work is split across threads, but there is a data race to increment the pointer A. However, if the threads happen to complete work in disjoint time intervals and in-order, we may get the correct result. 

Detailed justification:
This implementation is dependent on the threads processing in order, as thread 0, containing the 0 value of x, must occur first for the 0th element of A to be assigned 0. If any other thread is executed first, A cannot correct itself, as A is never decremented.
Thread ordering with OpenMP is not deterministic, and is certainly not guaranteed to be in order.

Further, there can be data race issues. If multiple threads are executed such that they all execute the first line, *A = x; before the second line, A++;, they will clobber each other’s outputs by overwriting what the other threads wrote in the same position.

On the slim chance (almost impossible, but possible nonetheless) that the threads are scheduled such that each access occurs sequentially, the output will be correct, so it is only “Sometimes Incorrect”.
\end{solution}



\end{parts}

\end{blocksection}